---
title: "Alcohol vs Seat choice"
author: "Valerie Rodriguez"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The box plot with fancy notch shows peoples seats from front, middle and back. Its observed that people who sit in the back on average drink far more than people who sit in the middle and front. People in the middle drink more than those in the front.  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The numerical data shows that on average there is a 4:0:1 ratio of people who drink that sit in back:front:middle. The average number of drinks for people who sit in the the back is 9 which is 3x larger than the average of the people sitting in the middle and is 9x the average of people who sit in the front.


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Since the p value is 0.000116 this exemplifies that the possibility of there being no difference in the amount people drink regarding there seating position is very unlikely.


## Conclusions


