---
title: "Alcohol vs Seat choice"
author: "Valerie Rodriguez"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The box plot with fancy notch shows peoples seats from front, middle and back. Its observed that people who sit in the back on average drink far more than people who sit in the middle and front. People in the middle drink more than those in the front.  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The numerical data shows that on average there is a 4:0:1 ratio of people who drink that sit in back:front:middle. The average number of drinks for people who sit in the the back is 9 which is 3x larger than the average of the people sitting in the middle and is 9x the average of people who sit in the front.


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Since the p value is 0.000116 this exemplifies that the possibility of there being no difference in the amount people drink regarding there seating position is very unlikely.


```{r}
plot(TukeyHSD(model1))
```

There isn't any difference between front and the middle. The only difference is between the back and the middle and the front and the back. This is known because the dotted line on 0 only goes through the confidence interval for front and middle. This does not happen for the other 2 categories.

## Conclusions

In conclusion the numerical data, inferential data and tukey graph all conclude that people who are seated in the back consume significantly more alcohol than those who sit in the middle and front. The numerical data showed a 9:3:1 ratio from back to front in the amount of drinks consumed. The inferential data confirmed this idea with a very small p value that dismissed the theory of there being no difference in all 3 rows. The Tukey data showed that the middle drank equal amount as the front.
